Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-02-06 analysis/paper/paper.Rmd
Corrected relative paths to source'd files.

```{r DataInput, eval=TRUE, echo=FALSE, cache=TRUE}
# if (system("git config user.email")=="mward2@swarthmore.edu") source("./scripts/data_retrievalSwarthmore.R")
# else source("./scripts/data_retrievalNPS.R")

#NOTE: working directory when knitting markup is /analysis/paper. So relative pathway needs to be ../scripts etc.
getwd()
source("./analysis/scripts/data_retrievalCSVs.R")
```

@@

```{r, eval=TRUE}
source("./analysis/scripts/data_exploration.R")
#source("../scripts/units_species.R")
```

>>>>

```{r DataInput, eval=TRUE, echo=FALSE, cache=TRUE}
# if (system("git config user.email")=="mward2@swarthmore.edu") 
#      source("./scripts/data_retrievalSwarthmore.R")
# else source("./scripts/data_retrievalNPS.R")

#NOTE: working directory when knitting markup is /analysis/paper. So relative pathway needs to be ../scripts etc.
print(getwd())
#source("./analysis/scripts/data_retrievalCSV.R")
source("../scripts/data_retrievalCSV.R") #JR added 2019 Feb 5, need '..' to reference relative parent directory.

```

@@

```{r, eval=TRUE}
#source("./analysis/scripts/data_exploration.R")
source("../scripts/data_exploration.R") # JR 2019 Feb 5 corrected relative pathname

#source("../scripts/units_species.R")
```
